`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-24 inst/manuscript/manuscript.rmd
Add another conclusion paragraph;

>>>>

Results from `flippant`-driven analysis track well prior manual analysis. 
Deviations observed may stem from algorithmic differences such as the fitting 
routine used (`flippant` uses the Nash variant of the Marquardt 
nonlinear least squares algorithm as implemented by @nash_nlmrt:_2014) and 
general handling of significant digits and rounding.
